% Enable hyperlinks
\setupinteraction
  [state=start,
  title={Cover Letter},
  subtitle={Full Stack Senior Software Engineer},
  author={Mohamed Bana},
  style=boldslanted,
  color=red,
  contrastcolor=]

% make chapter, section bookmarks visible when opening document
\placebookmarks[chapter, section, subsection, subsubsection, subsubsubsection, subsubsubsubsection][chapter, section]
\setupinteractionscreen[option=bookmark]
\setuptagging[state=start]


% use microtypography
\definefontfeature[default][default][script=latn, protrusion=quality, expansion=quality, itlc=yes, textitalics=yes, onum=yes, pnum=yes]
\definefontfeature[smallcaps][script=latn, protrusion=quality, expansion=quality, smcp=yes, onum=yes, pnum=yes]
\setupalign[hz,hanging]
\setupitaliccorrection[global, always]

\setupbodyfontenvironment[default][em=italic] % use italic as em, not slanted

\definefallbackfamily[mainface][rm][CMU Serif][preset=range:greek, force=yes]
\definefontfamily[mainface][rm][Latin Modern Roman]
\definefontfamily[mainface][mm][Latin Modern Math]
\definefontfamily[mainface][ss][Latin Modern Sans]
\definefontfamily[mainface][tt][Latin Modern Typewriter][features=none]
\setupbodyfont[mainface,11pt]

\setupwhitespace[small]

\setuphead[chapter]            [style=\tfd,header=empty]
\setuphead[section]            [style=\tfc]
\setuphead[subsection]         [style=\tfb]
\setuphead[subsubsection]      [style=\bf]
\setuphead[subsubsubsection]   [style=\sc]
\setuphead[subsubsubsubsection][style=\it]

\setuphead[chapter, section, subsection, subsubsection, subsubsubsection, subsubsubsubsection][number=no]

\definedescription
  [description]
  [headstyle=bold, style=normal, location=hanging, width=broad, margin=1cm, alternative=hanging]

\setupitemize[autointro]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setupthinrules[width=15em] % width of horizontal rules

\setupxtable[frame=off]
\setupxtable[head][topframe=on,bottomframe=on]
\setupxtable[body][]
\setupxtable[foot][bottomframe=on]

% --include-in-header
% \showframe
% % \showframe[edge]
% \showframe[cut]
% \setupbackgrounds[page][frame=on]

% % \showsetups
% % \showmakeup
% \showlayout
% \showframe
% \showlayoutcomponents
% \showgrid
% % \showboxes

\enableregime[utf]
\mainlanguage[en-GB]
\setuppapersize[A4][A4]

\usetypescriptfile[type-alegreya]
\usetypescript[alegreya]
\setupbodyfont[alegreya]
\setupbodyfont[9.5pt]
% \setupbodyfont[10pt]

\setuplayout[
  marking=on,
  height=fit,
  width=fit,
  % leftmargin=2mm,
  rightmargin=0mm,
  left=2mm,
  right=2mm,
  rightedge=2mm,
  rightedgedistance=0mm,
  top=2mm,
  topspace=2mm,
  topdistance=2mm,
  bottom=2mm,
  bottomdistance=0mm,
  % headerdistance=0mm,
  % footerdistance=0mm,
  % topspace=8mm,
  % header=16pt,
  header=0pt,
  footer=16pt,
  % backspace=0mm
  backspace=8pt,
]

% \setupwhitespace[flexible]
% \setupwhitespace[big]
% \setupblank[big]
\setupwhitespace[small]
\setupblank[small]
% \setupblank[none]

% \setupindenting[32pt]
% \indenting[yes,next]
% \setupindenting[yes,big]

% \setupitemize[autointro]    % prevent orphan list intro
% \setupitemize[indentnext=no]

% \setupheader[style=\smallcaps]
% \setupfooter[style=\smallcaps]
\setupheader[
    numberstyle=smallcaps,
    style=smallcaps,
    textstyle=smallcaps,
  ]
\setupfooter[
    numberstyle=smallcaps,
    style=smallcaps,
    textstyle=smallcaps,
  ]

\setuphead
  [section, subsection, subsubsection, subsubsubsection, subsubsubsubsection]
  [
    page=no,
    continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    number=yes,
    numberstyle=smallcaps,
    style=bold,
    textstyle=smallcaps,
    % header=none,
    % align={flushleft},
  ]

\setuphead
  [section]
  [
    % page=no,
    % continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    % number=yes,
    align={middle},
    % align={middle, hyphenated, verytolerant},
    % tolerance=verytolerant,
    % after={\startsectioncolumns},
    % % before={\nowhitespace},
    % before={\blank[none]\nowhitespace\hairline\blank[none]},
    % after={\blank[none]\nowhitespace\hairline\blank[none]},
    % beforesection={\blank[none]},
    % aftersection={\blank[none]},
    % aftersection={\stopsectioncolumns},
  ]
\setuphead
  [subsection]
  [
    % page=no,
    % continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    % number=yes,
    % align={flushleft, nothyphenated, verytolerant},
    % align={middle, hyphenated, verytolerant},
    % tolerance=verytolerant,
    align={middle},
    % before={\thinrule},
    % after={\thinrule},
    % strut=yes,
    % grid=yes,
    % beforesubsection={\blank[none]\nowhitespace},
    % aftersubsection={\blank[none]\nowhitespace\blank[none]},
  ]
\setuphead
  [subsubsection, subsubsubsection, subsubsubsubsection]
  [
    % page=no,
    % continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    % number=yes,
    % align={flushleft, hyphenated, verytolerant},
    % tolerance=verytolerant,
    align={flushleft},
    before={\blank[medium]},
    after={\blank[medium]},
    % after={},
    % before={\blank[big]},
    % % % before={\nowhitespace},
    % % after={\blank[none]},
    % % % after={\startsectioncolumns},
    % % beforesubsubsection={\blank[none]},
    % % aftersubsubsection={\blank[none]},
    % % % aftersection={\stopsectioncolumns},
  ]

\setuphead[section][
      page=no,
    continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    number=yes,
  before={\blank[big]\hrule}, after={\blank[none]\hrule\blank[big]}
  ]
\setuphead[subsection][
  page=no,
  continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
  number=yes,
  before={\blank[big]\hrule}, after={\blank[none]\hrule\blank[big]}
  ]

\setupfootertexts
  [Mohamed Bana — Curriculum Vitae, {\bf{Modified: }}{\currentdate[day,month,year]}]
  % []

  % []
% \setupfootertexts
%   [Mohamed Bana — Curriculum Vitae]
%   [{\bf{Last Updated: }}{\currentdate[weekday,{, },day,month,year], \currenttime[h,{\,:\,},m]}]
% \setupfootertexts
%   [{\bf{Last Updated: }}{\currentdate[weekday,month,day,{, },year]}]

  % alternative=doublesided,
  % ,state=stop
\setuppagenumbering[
  location={footer,right},style=smallcaps,textstyle=smallcaps,numberstyle=smallcaps,conversion=romannumerals
  ]
% \setuppagenumbering[location={footer,middle},style=smallcaps,conversion=romannumerals]

% \setupheader[state=high]
% \setupfooter[state=high]

% For \url:
\setupurl
   [color=red,
    style=\tf]

% For \goto and \from:
\setupinteraction
   [state=start,
    color=red,
    style=\tf]

\starttext
\startalignment[middle]
  {\tfd Cover Letter}
  \smallskip
  {\tfa Full Stack Senior Software Engineer}
  \smallskip
  {\tfa Mohamed Bana}
  \bigskip
\stopalignment
% --include-before-body=

% % \startcolumns
%   % [
%   %   n=2,
%   %   distance=5mm,
%   %   rule=on,
%   %   balance=yes,
%   %   align=flushleft,
%   % ]
%   % [
%   %   n=2,
%   %   balance=yes,
%   %   align=flushleft,
%   %   separator=rule,
%   % ]

% \startcolumns
%   [
%     n=2,
%     balance=no,
%     align=right,
%   ]

\subsection[title={Intro},reference={intro}]

I am a well-rounded Software Engineer, and I understand what it takes to
release a product having worked on the back-end, front-end, testing and
finally the deployment aspect of several products.

\subsection[title={Background},reference={background}]

A role involving web technologies hosted on a cloud-based backend. I've
worked on all the tiers of a software product, so I can appreciate the
different concerns expressed at each level. I feel the latest trend in
web technologies; quick prototyping, large selection of libraries, ease
of programming and its cross-platform support is where the future is
heading. This, distributed systems and big data algorithms are where I
am focusing my current efforts---all of which are equally interesting to
me.

I'm a well-rounded engineer and I'm able to see the delivery, from
beginning to end, of a software stack. This includes the building,
testing and continuous delivery of the solution. I have examples in my
repositories that demonstrate all these in a cloud environment:

\startitemize[packed]
\item
  Go/Golang backends.
\item
  Building frontends in JavaScript.
\item
  Complete end-to-end testing of the final project.
\item
  CI builds on the cloud.
\item
  Deployment on the cloud using Google Cloud Platform (GCP).
\item
  Containerising software using Docker.
\item
  Orchestrating the built containers using Kubernetes.
\stopitemize

\subsubsection[title={Job Preferences},reference={job-preferences}]

\subsubsubsection[title={Salary and notice
period},reference={salary-and-notice-period}]

I'm willing to negotiate on this as it depends on a few things, that
said:

\startitemize[packed]
\item
  If it's a contracting role, minimum of £580 per day.
\item
  If it's a permanent position, minimum of £90,000 per year.
\stopitemize

I'm available to start immediately.

\subsubsubsection[title={Work locations
considered},reference={work-locations-considered}]

Ideally, a remote role with an office in London.

If it's not fully remote, an office in East London would be perfect,
e.g., Canary Wharf, Aldgate (East).

\subsubsubsection[title={Key skills and preferred job
role},reference={key-skills-and-preferred-job-role}]

I'm flexible in terms of the choice of framework used, however, my ideal
role will involve (any of) the following:

\startitemize[packed]
\item
  Backend: Ideally Go/Golang as I have good experience with this.
\item
  Frontend: JavaScript or any language that targets JavaScript on the
  frontend side, my ideal choice would be TypeScript. I would prefer to
  use Vue.js as the underlying framework that the UI is built with.
\item
  Roles where Linux, Google Cloud Platform (GCP)/Azure/AWS, Docker and
  Kubernetes are being used. Open Banking would be a plus.
\item
  I'm up for learning more of Rust. It's just a hobby at the moment.
\stopitemize

{\bf Summary:} (Full Stack) Senior Software Engineer: Golang, Vue.js,
Linux, Docker, Docker-Compose, Kubernetes, Cloud Computing, Google Cloud
Computing (GCP).

\subsubsubsection[title={Any visa restrictions -- if applicable (ILR,
Tier 2, Dependant visa
etc)},reference={any-visa-restrictions-if-applicable-ilr-tier-2-dependant-visa-etc}]

\startitemize[packed]
\item
  {\bf Passport/Nationality:} I have a British Passport, national
  insurance number, British Citizenship etc.
\item
  {\bf Drivers Licence:} Full UK Driving Licence.
\item
  {\bf Background/Criminal Check:}
  \startitemize
  \item
    \useURL[url1][https://www.gov.uk/request-copy-criminal-record][][Basic
    Disclosure and Barring Service (DBS) check]\from[url1]: Certificate
    was issued on 31 July 2020.

    \startblockquote
    {\bf Police Records of Convictions, Cautions, Reprimands and
    Warnings:}

    NONE RECORDED
    \stopblockquote
  \item
    \useURL[url2][https://www.acro.police.uk/police_certificates.aspx][][Police
    Certificates - ACRO Criminal Records Office]\from[url2]: Certificate
    was issued on 18 February 2020.

    \startblockquote
    {\bf Summary of convictions and
    reprimands/warnings/cautions/impending prosecutions/under
    investigations held on UK police databases and disclosed in
    accordance with the ACRO stepdown model:}

    NO TRACE.
    \stopblockquote

    I have requested a new certificate and this should arrive between
    the 15th/28th of August 2020.
  \stopitemize
\stopitemize

I've a limited company called BANAIO LTD which I started in March 2017
and I've been a contractor since then. I would prefer to stick to
contracting but I will also consider a permanent position.

\subsubsubsection[title={Reason for looking for new
role},reference={reason-for-looking-for-new-role}]

Last contract finished on the 1st of January 2020.

Kind regards,

Mohamed Bana

\thinrule

\useURL[url3][https://bana.io]\from[url3] ---
\useURL[url4][mailto:m@bana.io][][m@bana.io]\from[url4] ---
\useURL[url5][tel:+44-7960-045-281][][+44-7960-045-281]\from[url5]

% --include-after-body
% \stopcolumns
\stoptext
