% Enable hyperlinks
\setupinteraction
  [state=start,
  title={Curriculum Vitae},
  subtitle={Full Stack Senior Software Engineer},
  author={Mohamed Bana},
  style=boldslanted,
  color=red,
  contrastcolor=]

% make chapter, section bookmarks visible when opening document
\placebookmarks[chapter, section, subsection, subsubsection, subsubsubsection, subsubsubsubsection][chapter, section]
\setupinteractionscreen[option=bookmark]
\setuptagging[state=start]


% use microtypography
\definefontfeature[default][default][script=latn, protrusion=quality, expansion=quality, itlc=yes, textitalics=yes, onum=yes, pnum=yes]
\definefontfeature[smallcaps][script=latn, protrusion=quality, expansion=quality, smcp=yes, onum=yes, pnum=yes]
\setupalign[hz,hanging]
\setupitaliccorrection[global, always]

\setupbodyfontenvironment[default][em=italic] % use italic as em, not slanted

\definefallbackfamily[mainface][rm][CMU Serif][preset=range:greek, force=yes]
\definefontfamily[mainface][rm][Latin Modern Roman]
\definefontfamily[mainface][mm][Latin Modern Math]
\definefontfamily[mainface][ss][Latin Modern Sans]
\definefontfamily[mainface][tt][Latin Modern Typewriter][features=none]
\setupbodyfont[mainface,9pt]

\setupwhitespace[medium]

\setuphead[chapter]            [style=\tfd,header=empty]
\setuphead[section]            [style=\tfc]
\setuphead[subsection]         [style=\tfb]
\setuphead[subsubsection]      [style=\bf]
\setuphead[subsubsubsection]   [style=\sc]
\setuphead[subsubsubsubsection][style=\it]

\setuphead[chapter, section, subsection, subsubsection, subsubsubsection, subsubsubsubsection][number=no]

\definedescription
  [description]
  [headstyle=bold, style=normal, location=hanging, width=broad, margin=1cm, alternative=hanging]

\setupitemize[autointro]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setupthinrules[width=15em] % width of horizontal rules

\setupxtable[frame=off]
\setupxtable[head][topframe=on,bottomframe=on]
\setupxtable[body][]
\setupxtable[foot][bottomframe=on]

% --include-in-header
% \showframe
% % \showframe[edge]
% \showframe[cut]
% \setupbackgrounds[page][frame=on]

% % \showsetups
% % \showmakeup
% \showlayout
% \showframe
% \showlayoutcomponents
% \showgrid
% % \showboxes

\enableregime[utf]
\mainlanguage[en-GB]
\setuppapersize[A4][A4]

\usetypescriptfile[type-alegreya]
\usetypescript[alegreya]
\setupbodyfont[alegreya]
\setupbodyfont[9.5pt]
% \setupbodyfont[10pt]

\setuplayout[
  marking=on,
  height=fit,
  width=fit,
  % leftmargin=2mm,
  rightmargin=0mm,
  left=2mm,
  right=2mm,
  rightedge=2mm,
  rightedgedistance=0mm,
  top=2mm,
  topspace=2mm,
  topdistance=2mm,
  bottom=2mm,
  bottomdistance=0mm,
  % headerdistance=0mm,
  % footerdistance=0mm,
  % topspace=8mm,
  % header=16pt,
  header=0pt,
  footer=16pt,
  % backspace=0mm
  backspace=8pt,
]

% \setupwhitespace[flexible]
% \setupwhitespace[big]
% \setupblank[big]
\setupwhitespace[small]
\setupblank[small]
% \setupblank[none]

% \setupindenting[32pt]
% \indenting[yes,next]
% \setupindenting[yes,big]

% \setupitemize[autointro]    % prevent orphan list intro
% \setupitemize[indentnext=no]

% \setupheader[style=\smallcaps]
% \setupfooter[style=\smallcaps]
\setupheader[
    numberstyle=smallcaps,
    style=smallcaps,
    textstyle=smallcaps,
  ]
\setupfooter[
    numberstyle=smallcaps,
    style=smallcaps,
    textstyle=smallcaps,
  ]

\setuphead
  [section, subsection, subsubsection, subsubsubsection, subsubsubsubsection]
  [
    page=no,
    continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    number=yes,
    numberstyle=smallcaps,
    style=bold,
    textstyle=smallcaps,
    % header=none,
    % align={flushleft},
  ]

\setuphead
  [section]
  [
    % page=no,
    % continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    % number=yes,
    align={middle},
    % align={middle, hyphenated, verytolerant},
    % tolerance=verytolerant,
    % after={\startsectioncolumns},
    % % before={\nowhitespace},
    % before={\blank[none]\nowhitespace\hairline\blank[none]},
    % after={\blank[none]\nowhitespace\hairline\blank[none]},
    % beforesection={\blank[none]},
    % aftersection={\blank[none]},
    % aftersection={\stopsectioncolumns},
  ]
\setuphead
  [subsection]
  [
    % page=no,
    % continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    % number=yes,
    % align={flushleft, nothyphenated, verytolerant},
    % align={middle, hyphenated, verytolerant},
    % tolerance=verytolerant,
    align={middle},
    % before={\thinrule},
    % after={\thinrule},
    % strut=yes,
    % grid=yes,
    % beforesubsection={\blank[none]\nowhitespace},
    % aftersubsection={\blank[none]\nowhitespace\blank[none]},
  ]
\setuphead
  [subsubsection, subsubsubsection, subsubsubsubsection]
  [
    % page=no,
    % continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    % number=yes,
    % align={flushleft, hyphenated, verytolerant},
    % tolerance=verytolerant,
    align={flushleft},
    before={\blank[medium]},
    after={\blank[medium]},
    % after={},
    % before={\blank[big]},
    % % % before={\nowhitespace},
    % % after={\blank[none]},
    % % % after={\startsectioncolumns},
    % % beforesubsubsection={\blank[none]},
    % % aftersubsubsection={\blank[none]},
    % % % aftersection={\stopsectioncolumns},
  ]

\setuphead[section][
      page=no,
    continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
    number=yes,
  before={\blank[big]\hrule}, after={\blank[none]\hrule\blank[big]}
  ]
\setuphead[subsection][
  page=no,
  continue=yes, % yes: If the section immediately follows a chapter it will be on the same page even though page=yes.
  number=yes,
  before={\blank[big]\hrule}, after={\blank[none]\hrule\blank[big]}
  ]

\setupfootertexts
  [Mohamed Bana — Curriculum Vitae, {\bf{Modified: }}{\currentdate[day,month,year]}]
  % []

  % []
% \setupfootertexts
%   [Mohamed Bana — Curriculum Vitae]
%   [{\bf{Last Updated: }}{\currentdate[weekday,{, },day,month,year], \currenttime[h,{\,:\,},m]}]
% \setupfootertexts
%   [{\bf{Last Updated: }}{\currentdate[weekday,month,day,{, },year]}]

  % alternative=doublesided,
  % ,state=stop
\setuppagenumbering[
  location={footer,right},style=smallcaps,textstyle=smallcaps,numberstyle=smallcaps,conversion=romannumerals
  ]
% \setuppagenumbering[location={footer,middle},style=smallcaps,conversion=romannumerals]

% \setupheader[state=high]
% \setupfooter[state=high]

% For \url:
\setupurl
   [color=red,
    style=\tf]

% For \goto and \from:
\setupinteraction
   [state=start,
    color=red,
    style=\tf]

\starttext
\startalignment[middle]
  {\tfd Curriculum Vitae}
  \smallskip
  {\tfa Full Stack Senior Software Engineer}
  \smallskip
  {\tfa Mohamed Bana}
  \bigskip
\stopalignment
% --include-before-body=

% % \startcolumns
%   % [
%   %   n=2,
%   %   distance=5mm,
%   %   rule=on,
%   %   balance=yes,
%   %   align=flushleft,
%   % ]
%   % [
%   %   n=2,
%   %   balance=yes,
%   %   align=flushleft,
%   %   separator=rule,
%   % ]

% \startcolumns
%   [
%     n=2,
%     balance=no,
%     align=right,
%   ]

\startplacetable[location=none]
\startxtable
\startxtablehead[head]
\startxrow
\startxcell[align=right] {\bf Contact} \stopxcell
\startxcell[align=left] {\bf Web} \stopxcell
\stopxrow
\stopxtablehead
\startxtablebody[body]
\startxrow
\startxcell[align=right]
\useURL[url1][tel:+44-7960-045-281][][+44-7960-045-281]\from[url1] (UK
Mobile) \stopxcell
\startxcell[align=left]
\useURL[url2][https://bana.io]\from[url2] \stopxcell
\stopxrow
\startxrow
\startxcell[align=right]
\useURL[url3][tel:+212-624-846-935][][+212-624-846-935]\from[url3]
(Moroccan Mobile) \stopxcell
\startxcell[align=left]
\useURL[url4][https://github.com/banaio]\from[url4] \stopxcell
\stopxrow
\stopxtablebody
\startxtablefoot[foot]
\startxrow
\startxcell[align=right]
\useURL[url5][mailto:m@bana.io][][m@bana.io]\from[url5] \stopxcell
\startxcell[align=left]
\useURL[url6][https://linkedin.com/in/mbana]\from[url6] \stopxcell
\stopxrow
\stopxtablefoot
\stopxtable
\stopplacetable

I am a well-rounded Software Engineer, with around 9-10 years of
Software Development experience. I understand what it takes to release a
product having worked on the back-end, front-end, testing and finally
the deployment aspect of several products.

\subsection[title={Work Experience},reference={work-experience}]

\subsubsection[title={Full Stack Go and Vue.js Developer,
\useURL[url7][https://www.openbanking.org.uk][][Open Banking
Limited]\from[url7], St Katharine's & Wapping, London, UK -
08/05/2018--01/01/2020},reference={full-stack-go-and-vue.js-developer-open-banking-limited-st-katharines-wapping-london-uk---0805201801012020}]

Working as a full stack developer at Open Banking on a tool that will
validate a bank's implementation of the OpenBanking API spec, see:

\startitemize[packed]
\item
  \useURL[url8][https://bitbucket.org/openbankingteam/conformance-suite]\from[url8]
\item
  \useURL[url9][https://hub.docker.com/u/openbanking/]\from[url9]
\stopitemize

{\bf Tech:} Go, Golang, Node.js,
\useURL[url10][https://vuejs.org/][][Vue.js]\from[url10],
\useURL[url11][https://vuex.vuejs.org/][][Vuex]\from[url11], Jest,
Docker, Docker Compose, Kubernetes,
\useURL[url12][https://openid.net/connect/][][OpenID
Connect]\from[url12], \useURL[url13][https://jwt.io/][][JSON Web Token
(JWT)]\from[url13],
\useURL[url14][http://kompose.io/][][Kompose]\from[url14],
\useURL[url15][https://circleci.com/][][CircleCI]\from[url15],
\useURL[url16][https://swagger.io/][][Swagger]\from[url16], WebSocket,
Bitbucket Pipelines, OpenAPI 3.0,
\useURL[url17][https://bitbucket.org/openbankingteam/conformance-suite]\from[url17],
\useURL[url18][https://hub.docker.com/u/openbanking/]\from[url18].

\subsubsection[title={Senior Engineer (contractor),
\useURL[url19][https://www.90poe.io/][][90POE - Ninety Percent of
Everything Limited]\from[url19], Marble Arch, London, UK -
01/02/2018--20/04/2018},reference={senior-engineer-contractor-90poe---ninety-percent-of-everything-limited-marble-arch-london-uk---0102201820042018}]

Worked at startup specialising in software that runs on ship on two
projects that were heavily Go-based.

{\bf \type{platform-document-storage-service}}: Document storage and
retrieval to be used by others services, so it's a core service. The
core of the service was written in Go and exposed using
\useURL[url20][https://grpc.io/][][gRPC]\from[url20] and http using
\useURL[url21][https://github.com/gorilla/mux][][go
gorilla/mux]\from[url21]. Both write and retrieve supported arbitrarily
large files which was achieved using gRPC unidirectional streams. The
underlying store was MongoDB's
\useURL[url22][https://docs.mongodb.com/manual/core/gridfs/][][GridsFS]\from[url22]
which I interfaced with using the Go driver
\useURL[url23][https://gopkg.in/mgo.v2][][mgo]\from[url23].

{\bf \type{auditing}}: Currently working on this. The service is
structured very similar to the preceding in that the underlying service
is exposed using gRPC but the top-level interface is done using
\useURL[url24][graphql.org][][GraphQL]\from[url24]. I wrote the GraphQL
server in go using
\useURL[url25][https://github.com/graph-gophers/graphql-go][][graphql-go]\from[url25].
The underlying store is in Postgres and the library I used to interact
with it is \useURL[url26][http://gorm.io/][][GORM]\from[url26].

{\bf Tech:} Go, Golang,
\useURL[url27][https://grpc.io/][][gRPC]\from[url27],
\useURL[url28][https://github.com/gorilla/mux][][go
gorilla/mux]\from[url28], Protocol Buffers,
\useURL[url29][http://gorm.io/][][GORM]\from[url29], MongoDB,
\useURL[url30][https://docs.mongodb.com/manual/core/gridfs/][][MongoDB
GridsFS]\from[url30],
\useURL[url31][https://gopkg.in/mgo.v2][][mgo]\from[url31],
\useURL[url32][graphql.org][][GraphQL]\from[url32],
\useURL[url33][https://github.com/graph-gophers/graphql-go][][graphql-go]\from[url33],
Docker, Docker Compose, Kubernetes, NodeJS, Jest,
\useURL[url34][https://concourse-ci.org/][][Concourse CI]\from[url34],
Postgres.

\subsubsection[title={Full Stack Developer (contractor),
\useURL[url35][https://www.rootcapital.co.uk][][Root Capital
LLP]\from[url35], London Bridge, London, UK -
09/10/2017--24/12/2017},reference={full-stack-developer-contractor-root-capital-llp-london-bridge-london-uk---0910201724122017}]

Worked as a full stack Node.js developer on the
\useURL[url36][https://mindsforlife.com/][][Minds for Life]\from[url36]
application, mainly on the forum.

{\bf Frontend:}

\startitemize[packed]
\item
  \type{react}, \type{react-redux},
  \useURL[url37][https://www.reactboilerplate.com/][][react-boilerplate]\from[url37].
\item
  Single Page Application (SPA) targeting mobile platforms.
\item
  \type{ES56} using most of the latest ES56 features; \type{async},
  \type{await}, \type{classes} etc.
\item
  Serveless and hosted on
  \useURL[url38][https://aws.amazon.com/s3/][][Amazon S3]\from[url38] as
  static assets, with
  \useURL[url39][http://aws.amazon.com/cloudfront/][][Amazon
  CloudFront]\from[url39] as the CDN.
\stopitemize

{\bf Backend:}

\startitemize[packed]
\item
  NodeJS server written in \type{ES6}, like the frontend.
\item
  \useURL[url40][http://koajs.com][][Koa]\from[url40].
\item
  MySQL as the datastore, using the
  \useURL[url41][http://knexjs.org/][][Knex.js]\from[url41] library.
\item
  Packaged as a set of \type{docker} containers.
\stopitemize

{\bf CI, Devops and Infrastructure:}

\startitemize[packed]
\item
  Services were packaged as containers. Used \type{docker} and
  \type{docker-compose} to start them.
\item
  Builds managed by \useURL[url42][https://semaphoreci.com][][Semaphore
  CI]\from[url42] and
  \useURL[url43][http://www.wercker.com/][][Wercker]\from[url43].
\stopitemize

{\bf Tech:} JavaScript, ES6, Node.js, react, react-redux,
\useURL[url44][https://www.reactboilerplate.com/][][react-boilerplate]\from[url44],
Webpack, \useURL[url45][http://koajs.com][][Koa]\from[url45],
\useURL[url46][http://knexjs.org/][][Knex.js]\from[url46], Sequel Pro,
Docker, Docker Compose, Kubernetes,
\useURL[url47][https://semaphoreci.com][][Semaphore CI]\from[url47],
\useURL[url48][http://www.wercker.com/][][Wercker]\from[url48],
\useURL[url49][https://aws.amazon.com/s3/][][Amazon S3]\from[url49],
\useURL[url50][http://aws.amazon.com/cloudfront/][][Amazon
CloudFront]\from[url50]

\subsubsection[title={Full Stack Node Developer (contractor),
\useURL[url51][https://www.lloydsbankinggroup.com][][Lloyds Banking
Group PLC]\from[url51], London Bridge, London, UK -
20/03/2017--22/05/2017},reference={full-stack-node-developer-contractor-lloyds-banking-group-plc-london-bridge-london-uk---2003201722052017}]

{\bf NodeJS - JavaScript:}

\startitemize[packed]
\item
  Loopback for server-side of the code.
\item
  ES5/6-based code base.
\stopitemize

{\bf Monitoring/Devops/Misc:}

\startitemize[packed]
\item
  Splunk and sending logs via
  (\useURL[url52][https://en.wikipedia.org/wiki/Syslog]\from[url52]) a
  LogDrain service available on Bluemix.
\item
  Gerrit for managing code. CI:
\item
  Jenkins: Configuring, managing and installing.
\item
  Jenkins 2: Same as previous plus writing pipeline scripts.
\stopitemize

{\bf Tech:} JavaScript, Node.js, ES5/6-based code base,
\useURL[url53][https://loopback.io][][LoopBack]\from[url53] for
server-side of the code,
\useURL[url54][https://en.wikipedia.org/wiki/Syslog][][SysLog]\from[url54],
\useURL[url55][http://www.splunk.com][][Splunk]\from[url55],
\useURL[url56][https://www.jenkins.io][][Jenkins]\from[url56],
\useURL[url57][https://www.jenkins.io/2.0][][Jenkins 2]\from[url57],
\useURL[url58][https://www.gerritcodereview.com/][][Gerrit Code
Review]\from[url58],
\useURL[url59][https://en.wikipedia.org/wiki/Bluemix][][IBM
Bluemix]\from[url59]

\subsubsection[title={Senior Front-End Engineer,
\useURL[url60][https://synthace.com][][Synthace Ltd.]\from[url60],
King's Cross, London, UK -
13/04/2016--04/11/2016},reference={senior-front-end-engineer-synthace-ltd.-kings-cross-london-uk---1304201604112016}]

Did a fair amount of architectural UI work:

\startitemize[packed]
\item
  JWT-based authentication: Implemented most, if not all, of the
  authentication related UI features. Polymer didn't have an
  authentication module as it's fairly new requiring me to re-implement
  this feature.
\item
  API interactions: I introduced Swagger JS and did the conversion from
  plain XHR to Promises, and ensured API was in-sync with the state of
  the authentication.
\item
  Updates via the Web Socket for notifications and async task updates:
  STOMP Over WebSocket.
\item
  Bootstrapped the testing using Web Component Tester.
\item
  Deciding on the build, test and hosting strategy, e.g., hosting our
  own CDN using Azure.
\item
  Performance: 1) pushed to have HTTP/2 enabled, and prototyped, on our
  custom server written in Go, 2) implemented lazy-loading of our Web
  Components which are included using HTML Imports, 3) Significantly
  improved UI build scripts; went from a somewhat un-deterministic build
  to one that almost always runs.
\item
  Introduced ES6 to the code-base, and moving to defining Polymer
  elements using ES6 classes.
\item
  Misc: libraries/utils to ease UI development.
\stopitemize

We deploy Docker images to our Kubernetes cluster running in Azure
using:

\startitemize[packed]
\item
  Docker: Fairly comfortable using this.
\item
  Kubernetes: I've done deployments of dev branches, so I understand the
  deployment model, navigating the Kubernetes dashboard and crude
  command line interactions, e.g., port-forwarding of the service the
  pod is running from the cluster to the local machine.
\stopitemize

I'm finishing up on adding support for our language Antha to Monaco
Editor, the editor that powers Visual Studio Code.

Since this is a startup I have done a fair amount of work and I have
been given a fair share of responsibility, more so than any of my prior
roles.

{\bf Tech:} JavaScript, ES6,
\useURL[url61][https://www.polymer-project.org][][Polymer
Project]\from[url61],
\useURL[url62][https://www.webcomponents.org][][Web
Components]\from[url62], TypeScript, VSCode, Azure, Docker, Kubernetes,
Go,
\useURL[url63][https://github.com/Polymer/web-component-tester][][Polymer
Web Component Tester]\from[url63], Git, Swagger.

\subsubsection[title={Developer,
\useURL[url64][https://www.ig.com/uk][][IG Index Ltd.]\from[url64]
Cannon Bridge, London, UK -
09-2014--18/02/2016},reference={developer-ig-index-ltd.-cannon-bridge-london-uk---09-201418022016}]

\subsubsubsection[title={JavaScript
Developer},reference={javascript-developer}]

\startitemize[packed]
\item
  {\em Price & Indicator Alerts:} My main responsibility was handling
  the UI aspect---setting, configuring, triggering---of the various
  Alerts we support, from the basic Price Alert to Technical Indicators
  such as RSI and Moving Average. {\bf Tech New:} Modern UI powered by
  ES2015 (Babel), Ember.js, Handlebars and Less. The UI was then
  composed of isolated and reusable Ember components. Runs on a NodeJS
  server, managed with npm and bower, and version controlled using Git.
  Integration and unit tests written in Mocha then run using Karma.
  {\bf Tech Old:} Vanilla JavaScript using an in-house framework when
  changing the previous UI.
\item
  {\em Charts:} Assisted in the conversion of the Adobe Flex Real Time
  Charts to an SVG-based version. {\bf Tech:} d3 and tested like above.
\item
  {\em Deeplinking:} A hashed action link, like typical deeplinks, that
  we send to our Clients which then launches the mobile IG app, or
  directs them to the app store for the device with the IG app
  pre-selected. Upon login the action is carried out automatically. I
  did the bulk of the work with the team lead overseeing it. {\bf Tech:}
  Java 8, Spring and acceptance tested using Cucumber. Redirecting and
  launching of the IG app was done using vanilla JavaScript.
\stopitemize

\subsubsection[title={Software Developer,
\useURL[url65][https://www.itrsgroup.com][][ITRS (International Trading
Room Software) Group Ltd.]\from[url65] Moorgate, London, UK -
02-2010--09-2014},reference={software-developer-itrs-international-trading-room-software-group-ltd.-moorgate-london-uk---02-201009-2014}]

\subsubsubsection[title={JavaScript (UI) Developer,
01/2014--09/2014},reference={javascript-ui-developer-012014092014}]

UI for the next generation of the product which is built around, loosely
speaking, a real-time distributed analytics store. The aim is for the
old system to stream data to the new system so we can provide all the
great visualizations available in the HTML ecosystem, which was not
achievable in a reasonable amount of time in Swing.

The code is entirely modularized using RequireJS so we can test each
viewmodel without creating a view, we then test the entire UI
(end-to-end tests) using WebDriverJS.

Some Java/C coding required to write NodeJS bindings to interact with
the store. We evaluated several frameworks, Angular, Batman and
KnockoutJS, by writing prototype applications that connected to our
backend for a period of roughly 4-6 months before we chose to settle on
Knockout.js.

{\bf Tech:} JavaScript, NodeJS, Node-WebKit, Durandal, KnockoutJS,
RequireJS, Git, Jasmine, Protractor (WebDriverJS), Jenkins, Bower,
HTML5, CSS, LoopBack.io.

\subsubsubsection[title={Java (UI) Developer -
07/2012--12/2013},reference={java-ui-developer---072012122013}]

Worked with two developers and one QA member on a new Swing UI, ACLite,
that uses our new streaming-based API to access Geneos data, for more
info. see
\useURL[url66][https://resources.itrsgroup.com/OpenAccess]\from[url66].
We access data from a fault-tolerant Cluster that is built on a set of
distributed nodes. The system we coded against is somewhat similar to
the Amazon distributed key/value store, DynamoDB, except with support
for streaming, so I am familiar with dealing with distributed systems.

{\bf Tech:} Java, Maven, Swing, Eclipse, Jenkins, Git, Vagrant.

\subsubsubsection[title={C++ Developer -
02/2010--06/2012},reference={c-developer---022010062012}]

Spent one year with Run The Business (RTB) team, a team set-up to fix
critical bugs that Customers encounter. A very challenging role which
requires all-around product knowledge, good debugging skills and being
able to liaise with our Support staff in dealing with the Customers.
Prior to this I was one of three developers working in the Transactions
and Latency Monitoring team (part of the backend team) doing core C++.
We wrote and maintained the following plug-ins that are part of the
Geneos suite:

\startitemize[n,packed][stopper=.]
\item
  \useURL[url67][https://docs.itrsgroup.com/docs/geneos/5.1.0/Netprobe/trading_fix/fix.html][][Geneos
  FIX plug-in]\from[url67]: Monitors FIX (protocol) messages.
\item
  \useURL[url68][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/feedadapter_ug.html][][Feed
  Latency Monitoring Plug-In]\from[url68]: Monitors feeds and calculates
  latency of instruments and fields across the monitored feeds.
\item
  \useURL[url69][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/latency_monitoring/message_tracker/fix_adapter.html][][Latency
  Monitoring - Message Tracker FIX adapter]\from[url69]: Tracks,
  generally, FIX messages across several checkpoints.
\item
  \useURL[url70][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/mdm_ug.html][][Market
  Data Monitor]\from[url70]: See below. And bespoke plug-ins written for
  specific firms.
\stopitemize

We also maintained several non-finance specific plug-ins. I ported
another bespoke plug-in called Price Latency Monitor (provides latency
figures for bonds) to MS VC++ when I worked on this team. Projects:

\startitemize[packed]
\item
  I converted the Windows version of the entire product suite from
  Visual Studio 2005 to 2010.
\item
  I wrote the Market Data Reliability plug-in. This plug-in connects to
  the Patsystem's Trading API (<www.patsystems.com>) to monitor
  commodity prices, using their C API, to determine if prices are
  \quote{stale}.
\item
  I ported a significant part of our product to Solaris x86-64 (64-bit
  non-sparc architecture).
\stopitemize

{\bf Tech:} C++, STL, Boost, Visual Studio, Linux/Unix, GDB, DBX, Make,
Configure, XML, XPath, CPPUnit,
\useURL[url67][https://en.wikipedia.org/wiki/Financial_Information_eXchange][][Financial
Information eXchange (FIX) protocol]\from[url67],
\useURL[url68][https://docs.itrsgroup.com/docs/geneos/5.1.0/Netprobe/trading_fix/fix.html][][Geneos
FIX plug-in]\from[url68],
\useURL[url69][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/feedadapter_ug.html][][Feed
Latency Monitoring Plug-In]\from[url69],
\useURL[url70][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/latency_monitoring/message_tracker/fix_adapter.html][][Latency
Monitoring - Message Tracker FIX adapter]\from[url70],
\useURL[url71][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/mdm_ug.html][][Market
Data Monitor]\from[url71],
\useURL[url72][https://docs.itrsgroup.com/docs/geneos/5.1.0/Netprobe/trading_pats/pats-status.html][][Geneos
PATS-STATUS Plug-In]\from[url72],
\useURL[url73][www.patsystems.com][][Patsystem's Trading
API]\from[url73].

\subsubsection[title={Software Developer Intern, then Tester, Thomson
Reuters. Canary Wharf, London, UK -
05-2009--11-2009},reference={software-developer-intern-then-tester-thomson-reuters.-canary-wharf-london-uk---05-200911-2009}]

\subsubsubsection[title={C\# Developer},reference={c-developer}]

One of four developers working on a search and navigation interface to
Global Product Search. Full life-cycle of development; requirements
engineering, analysis and design to implementation, testing and
deployment.

{\bf Tech:} C\#, Silverlight 3.0, MS SQL Server 2005, LINQ, Web Services
(WCF), XML and Visual Studio 2008. I handled deployment using
CruiseControl.NET.

\subsubsubsection[title={Tester},reference={tester}]

User Acceptance Testing of the latest release of Thomson Reuter's 3000
Extra, then called UTAH, now called Eikon. UTAH combines the data from
Thomson and Reuters. My primary responsibilities were to validate the
end product against pre-defined requirements/workflows. 1. Worked on
Thomson Reuters project UTAH as part of a large team. 2. Tasks included
testing, observing, documenting software bugs, issues and errors before
final release of Utah. 3. Testing was done over multiple iterations.

\subsection[title={Education},reference={education}]

\startitemize[packed]
\item
  {\bf 2005-2008:} BSc Computer Science (2.1), City, University of
  London.
\item
  {\bf 2008-2009:} MSc Software Systems Engineering (Attended),
  University College London, and Trading & Financial Market Structure
  module, London Business School.
\stopitemize

\subsection[title={Additional
Information},reference={additional-information}]

\subsubsection[title={Misc},reference={misc}]

\startitemize[packed]
\item
  {\bf Passport/Nationality:} I have a British Passport.
\item
  {\bf Drivers Licence:} Full UK Driving Licence.
\item
  {\bf Background/Criminal Check:}
  \startitemize
  \item
    \useURL[url74][https://www.gov.uk/request-copy-criminal-record][][Basic
    Disclosure and Barring Service (DBS) check]\from[url74]: Certificate
    was issued on 31 July 2020.

    \startblockquote
    {\bf Police Records of Convictions, Cautions, Reprimands and
    Warnings:}

    NONE RECORDED
    \stopblockquote
  \item
    \useURL[url75][https://www.acro.police.uk/police_certificates.aspx][][Police
    Certificates - ACRO Criminal Records Office]\from[url75]:
    Certificate was issued on 18 February 2020.

    \startblockquote
    {\bf Summary of convictions and
    reprimands/warnings/cautions/impending prosecutions/under
    investigations held on UK police databases and disclosed in
    accordance with the ACRO stepdown model:}

    NO TRACE.
    \stopblockquote

    I have requested a new certificate and this should arrive between
    the 15th/28th of August 2020.
  \stopitemize
\stopitemize

\subsubsection[title={Languages},reference={languages}]

\startitemize[packed]
\item
  {\bf English and Swahili:} Native.
\item
  {\bf Arabic:} Intermediate. I own an apartment in Marrakech, Morocco.
  I have lived in Cairo, Egypt and have travelled several times to the
  UAE.
\stopitemize

% --include-after-body
% \stopcolumns
\stoptext
