\startplacetable[location=none]
\startTABLE
\startTABLEhead
\NC[align=right,width={0.63\textwidth}] Contact
\NC[align=left,width={0.37\textwidth}] Web
\NC\NR
\stopTABLEhead
\startTABLEbody
\stopTABLEbody
\startTABLEfoot
\NC[align=right,width={0.63\textwidth}] 📱:
\useURL[url1][tel:+44-7960-045-281][][+44-7960-045-281]\from[url1] (UK
Mobile)📱:
\useURL[url2][tel:+212-624-846-935][][+212-624-846-935]\from[url2]
(Moroccan Mobile)📱:
\useURL[url3][tel:+212-808-526-830][][+212-808-526-830]\from[url3]
(Moroccan Landline)📧:
\useURL[url4][mailto:m@bana.io][][m@bana.io]\from[url4]📧:
\useURL[url5][mailto:b@bana.io][][b@bana.io]\from[url5]
\NC[align=left,width={0.37\textwidth}]
\useURL[url6][https://bana.io]\from[url6]
\useURL[url7][https://github.com/banaio]\from[url7]
\useURL[url8][https://linkedin.com/in/mbana]\from[url8]
\NC\NR
\stopTABLEfoot
\stopTABLE
\stopplacetable

I am a well-rounded Software Engineer, with around 9-10 years of
Software Development experience. I understand what it takes to release a
product having worked on the back-end, front-end, testing and finally
the deployment aspect of several products.

\subsection[title={Work Experience},reference={work-experience}]

\subsubsection[title={Full Stack Go and Vue.js Developer,
\useURL[url9][https://www.openbanking.org.uk][][Open Banking
Limited]\from[url9], St Katharine's & Wapping, London, UK -
08/05/2018--01/01/2020},reference={full-stack-go-and-vue.js-developer-open-banking-limited-st-katharines-wapping-london-uk---0805201801012020}]

{\bf Tech:} Go, Golang, Node.js,
\useURL[url10][https://vuejs.org/][][Vue.js]\from[url10],
\useURL[url11][https://vuex.vuejs.org/][][Vuex]\from[url11], Jest,
Docker, Docker Compose, Kubernetes,
\useURL[url12][https://openid.net/connect/][][OpenID
Connect]\from[url12], \useURL[url13][https://jwt.io/][][JSON Web Token
(JWT)]\from[url13],
\useURL[url14][http://kompose.io/][][Kompose]\from[url14],
\useURL[url15][https://circleci.com/][][CircleCI]\from[url15],
\useURL[url16][https://swagger.io/][][Swagger]\from[url16], WebSocket,
Bitbucket Pipelines, OpenAPI 3.0,
\useURL[url17][https://bitbucket.org/openbankingteam/conformance-suite]\from[url17],
\useURL[url18][https://hub.docker.com/u/openbanking/]\from[url18].

\subsubsection[title={Senior Engineer (contractor),
\useURL[url19][https://www.90poe.io/][][90POE - Ninety Percent of
Everything Limited]\from[url19], Marble Arch, London, UK -
01/02/2018--20/04/2018},reference={senior-engineer-contractor-90poe---ninety-percent-of-everything-limited-marble-arch-london-uk---0102201820042018}]

{\bf Tech:} Go, Golang,
\useURL[url20][https://grpc.io/][][gRPC]\from[url20],
\useURL[url21][https://github.com/gorilla/mux][][go
gorilla/mux]\from[url21], Protocol Buffers,
\useURL[url22][http://gorm.io/][][GORM]\from[url22], MongoDB,
\useURL[url23][https://docs.mongodb.com/manual/core/gridfs/][][MongoDB
GridsFS]\from[url23],
\useURL[url24][https://gopkg.in/mgo.v2][][mgo]\from[url24],
\useURL[url25][graphql.org][][GraphQL]\from[url25],
\useURL[url26][https://github.com/graph-gophers/graphql-go][][graphql-go]\from[url26],
Docker, Docker Compose, Kubernetes, NodeJS, Jest,
\useURL[url27][https://concourse-ci.org/][][Concourse CI]\from[url27],
Postgres.

\subsubsection[title={Full Stack Developer (contractor),
\useURL[url28][https://www.rootcapital.co.uk][][Root Capital
LLP]\from[url28], London Bridge, London, UK -
09/10/2017--24/12/2017},reference={full-stack-developer-contractor-root-capital-llp-london-bridge-london-uk---0910201724122017}]

{\bf Tech:} JavaScript, ES6, Node.js, react, react-redux,
\useURL[url29][https://www.reactboilerplate.com/][][react-boilerplate]\from[url29],
Webpack, \useURL[url30][http://koajs.com][][Koa]\from[url30],
\useURL[url31][http://knexjs.org/][][Knex.js]\from[url31], Sequel Pro,
Docker, Docker Compose, Kubernetes,
\useURL[url32][https://semaphoreci.com][][Semaphore CI]\from[url32],
\useURL[url33][http://www.wercker.com/][][Wercker]\from[url33],
\useURL[url34][https://aws.amazon.com/s3/][][Amazon S3]\from[url34],
\useURL[url35][http://aws.amazon.com/cloudfront/][][Amazon
CloudFront]\from[url35]

\subsubsection[title={Full Stack Node Developer (contractor),
\useURL[url36][https://www.lloydsbankinggroup.com][][Lloyds Banking
Group PLC]\from[url36], London Bridge, London, UK -
20/03/2017--22/05/2017},reference={full-stack-node-developer-contractor-lloyds-banking-group-plc-london-bridge-london-uk---2003201722052017}]

{\bf Tech:} JavaScript, Node.js, ES5/6-based code base,
\useURL[url37][https://loopback.io][][LoopBack]\from[url37] for
server-side of the code,
\useURL[url38][https://en.wikipedia.org/wiki/Syslog][][SysLog]\from[url38],
\useURL[url39][http://www.splunk.com][][Splunk]\from[url39],
\useURL[url40][https://www.jenkins.io][][Jenkins]\from[url40],
\useURL[url41][https://www.jenkins.io/2.0][][Jenkins 2]\from[url41],
\useURL[url42][https://www.gerritcodereview.com/][][Gerrit Code
Review]\from[url42],
\useURL[url43][https://en.wikipedia.org/wiki/Bluemix][][IBM
Bluemix]\from[url43]

\subsubsection[title={Senior Front-End Engineer,
\useURL[url44][https://synthace.com][][Synthace Ltd.]\from[url44],
King's Cross, London, UK -
13/04/2016--04/11/2016},reference={senior-front-end-engineer-synthace-ltd.-kings-cross-london-uk---1304201604112016}]

{\bf Tech:} JavaScript, ES6,
\useURL[url45][https://www.polymer-project.org][][Polymer
Project]\from[url45],
\useURL[url46][https://www.webcomponents.org][][Web
Components]\from[url46], TypeScript, VSCode, Azure, Docker, Kubernetes,
Go,
\useURL[url47][https://github.com/Polymer/web-component-tester][][Polymer
Web Component Tester]\from[url47], Git, Swagger.

\subsubsection[title={Developer,
\useURL[url48][https://www.ig.com/uk][][IG Index Ltd.]\from[url48]
Cannon Bridge, London, UK -
09-2014--18/02/2016},reference={developer-ig-index-ltd.-cannon-bridge-london-uk---09-201418022016}]

\subsubsubsection[title={JavaScript
Developer},reference={javascript-developer}]

\startitemize[packed]
\item
  {\em Price & Indicator Alerts:} My main responsibility was handling
  the UI aspect---setting, configuring, triggering---of the various
  Alerts we support, from the basic Price Alert to Technical Indicators
  such as RSI and Moving Average. {\bf Tech New:} Modern UI powered by
  ES2015 (Babel), Ember.js, Handlebars and Less. The UI was then
  composed of isolated and reusable Ember components. Runs on a NodeJS
  server, managed with npm and bower, and version controlled using Git.
  Integration and unit tests written in Mocha then run using Karma.
  {\bf Tech Old:} Vanilla JavaScript using an in-house framework when
  changing the previous UI.
\item
  {\em Charts:} Assisted in the conversion of the Adobe Flex Real Time
  Charts to an SVG-based version. {\bf Tech:} d3 and tested like above.
\item
  {\em Deeplinking:} A hashed action link, like typical deeplinks, that
  we send to our Clients which then launches the mobile IG app, or
  directs them to the app store for the device with the IG app
  pre-selected. Upon login the action is carried out automatically. I
  did the bulk of the work with the team lead overseeing it. {\bf Tech:}
  Java 8, Spring and acceptance tested using Cucumber. Redirecting and
  launching of the IG app was done using vanilla JavaScript.
\stopitemize

\subsubsection[title={Software Developer,
\useURL[url49][https://www.itrsgroup.com][][ITRS (International Trading
Room Software) Group Ltd.]\from[url49] Moorgate, London, UK -
02-2010--09-2014},reference={software-developer-itrs-international-trading-room-software-group-ltd.-moorgate-london-uk---02-201009-2014}]

\subsubsubsection[title={JavaScript (UI) Developer,
01/2014--09/2014},reference={javascript-ui-developer-012014092014}]

{\bf Tech:} JavaScript, NodeJS, Node-WebKit, Durandal, KnockoutJS,
RequireJS, Git, Jasmine, Protractor (WebDriverJS), Jenkins, Bower,
HTML5, CSS, LoopBack.io.

\subsubsubsection[title={Java (UI) Developer -
07/2012--12/2013},reference={java-ui-developer---072012122013}]

{\bf Tech:} Java, Maven, Swing, Eclipse, Jenkins, Git, Vagrant.

\subsubsubsection[title={C++ Developer -
02/2010--06/2012},reference={c-developer---022010062012}]

{\bf Tech:} C++, STL, Boost, Visual Studio, Linux/Unix, GDB, DBX, Make,
Configure, XML, XPath, CPPUnit,
\useURL[url50][https://en.wikipedia.org/wiki/Financial_Information_eXchange][][Financial
Information eXchange (FIX) protocol]\from[url50],
\useURL[url51][https://docs.itrsgroup.com/docs/geneos/5.1.0/Netprobe/trading_fix/fix.html][][Geneos
FIX plug-in]\from[url51],
\useURL[url52][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/feedadapter_ug.html][][Feed
Latency Monitoring Plug-In]\from[url52],
\useURL[url53][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/latency_monitoring/message_tracker/fix_adapter.html][][Latency
Monitoring - Message Tracker FIX adapter]\from[url53],
\useURL[url54][https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/mdm_ug.html][][Market
Data Monitor]\from[url54],
\useURL[url55][https://docs.itrsgroup.com/docs/geneos/5.1.0/Netprobe/trading_pats/pats-status.html][][Geneos
PATS-STATUS Plug-In]\from[url55],
\useURL[url56][www.patsystems.com][][Patsystem's Trading
API]\from[url56].

\subsubsection[title={Software Developer Intern, then Tester, Thomson
Reuters. Canary Wharf, London, UK -
05-2009--11-2009},reference={software-developer-intern-then-tester-thomson-reuters.-canary-wharf-london-uk---05-200911-2009}]

\subsubsubsection[title={C\# Developer},reference={c-developer}]

{\bf Tech:} C\#, Silverlight 3.0, MS SQL Server 2005, LINQ, Web Services
(WCF), XML and Visual Studio 2008. I handled deployment using
CruiseControl.NET.

\subsubsubsection[title={Tester},reference={tester}]

User Acceptance Testing of the latest release of Thomson Reuter's 3000
Extra, then called UTAH, now called Eikon. UTAH combines the data from
Thomson and Reuters. My primary responsibilities were to validate the
end product against pre-defined requirements/workflows. 1. Worked on
Thomson Reuters project UTAH as part of a large team. 2. Tasks included
testing, observing, documenting software bugs, issues and errors before
final release of Utah. 3. Testing was done over multiple iterations.

\subsection[title={Education},reference={education}]

\startplacetable[location=none]
\startTABLE
\startTABLEhead
\NC[width={0.28\textwidth}] 2005-2008
\NC[width={0.72\textwidth}] 2008-2009
\NC\NR
\stopTABLEhead
\startTABLEbody
\stopTABLEbody
\startTABLEfoot
\NC[width={0.28\textwidth}] BSc Computer Science (2.1), City, University
of London.
\NC[width={0.72\textwidth}] MSc Software Systems Engineering (Attended),
University College London, and Trading & Financial Market Structure
module, London Business School.
\NC\NR
\stopTABLEfoot
\stopTABLE
\stopplacetable

\subsection[title={Information},reference={information}]

I am looking for a role involving web technologies hosted on a
cloud-based backend. I've worked on all the tiers of a software product,
so I can appreciate the different concerns expressed at each level. I
feel the latest trend in web technologies; quick prototyping, large
selection of libraries, ease of programming and its cross-platform
support is where the future is heading. This, distributed systems and
big data algorithms are where I am focusing my current efforts---all of
which are equally interesting to me.

\subsubsection[title={Technology Stack},reference={technology-stack}]

I'm flexible in terms of the choice of framework used, however, my ideal
role will involve (any of) the following:

\startitemize[packed]
\item
  Backend: Ideally Go/Golang as I have good experience with this.
\item
  Frontend: JavaScript or any language that targets JavaScript on the
  frontend side, my ideal choice would be TypeScript. I would prefer to
  use Vue.js as the underlying framework that the UI is built with.
\item
  Roles where Linux, Google Cloud Platform/Azure/AWS, Docker and
  Kubernetes are being used. Open Banking would be a plus.
\item
  I'm up for learning more of Rust. It's just a hobby at the moment.
\stopitemize

\subsubsection[title={Enumeration and Job
Preferences},reference={enumeration-and-job-preferences}]

\startitemize[packed]
\item
  {\bf Rate:} I'm seeking a daily rate of >£580 per day. I'm willing to
  negotiate on this.
\item
  {\bf Location:} I'm looking for work in the UK, ideally in London as
  that is where I mainly live.
\item
  {\bf Start Date:} I'm available to start immediately.
\item
  {\bf Job Type:} I've a limited company called BANAIO LTD which I
  started in March 2017 and I've been a contractor since then. I would
  prefer to stick to contracting but I will also consider a permanent
  position.
\stopitemize

\subsection[title={Additional
Information},reference={additional-information}]

\startplacetable[location=none]
\startTABLE
\startTABLEhead
\NC[width={0.16\textwidth}] Misc
\NC[width={0.84\textwidth}] Languages
\NC\NR
\stopTABLEhead
\startTABLEbody
\NC[width={0.16\textwidth}] I have a British Passport.
\NC[width={0.84\textwidth}] {\bf English and Swahili:} Native.
\NC\NR
\stopTABLEbody
\startTABLEfoot
\NC[width={0.16\textwidth}] Full UK Driving Licence.
\NC[width={0.84\textwidth}] {\bf Arabic:} Intermediate. I own an
apartment in Marrakech, Morocco. I have lived in Cairo, Egpyt and have
travelled several times to the UAE.
\NC\NR
\stopTABLEfoot
\stopTABLE
\stopplacetable
