% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{geometry}
\geometry{
    heightrounded,
    a4paper,
    inner=4mm,
    outer=4mm,
    top=4mm,
    bottom=14mm,
}

\usepackage{fontspec}
\defaultfontfeatures{
    Ligatures = { Required, Common, Contextual , Rare },
    Numbers = OldStyle,
    Mapping = tex-text,
}
% working
% \setmainfont{Iosevka Fixed SS05}[
%     Scale=0.7,
% ]
% \setsansfont{Iosevka Fixed SS05}[
%     Scale=0.7,
% ]
% \setmonofont{Iosevka Fixed SS05}[
%     Scale=0.7,
% ]

\setmainfont{Iosevka Fixed SS05}[
    Scale=0.8,
]
\setsansfont{Iosevka Fixed SS05}[
    Scale=0.8,
]
\setmonofont{Iosevka Fixed SS05}[
    Scale=0.8,
]

\usepackage{multicol}


% \setmainfont[Scale=0.3,Mapping=tex-text,Ligatures={Common,Rare,TeX},Scale=MatchLowercase,Numbers=OldStyle]{Iosevka Regular}
% \setmainfont[Scale=MatchLowercase,Numbers=OldStyle,Ligatures={Common,Rare,Historic},Style=Swash]{Iosevka}

% \defaultfontfeatures{Mapping=tex-text,Ligatures={Common,Rare,TeX},Scale=MatchLowercase,Numbers=OldStyle}



% \setmainfont{/home/mbana/.fonts/truetype/iosevka-fonts/iosevka-regular.ttf}
% \setmainfont{/usr/share/fonts/iosevka-term-fonts/iosevka-term-regular.ttf}



% % \defaultfontfeatures{Mapping=tex-text,Numbers={OldStyle,Lowercase,Proportional},Ligatures={Common,Rare,TeX},Style=Historic}
% \defaultfontfeatures{Mapping=tex-text,Ligatures={Common,Rare,TeX},Scale=MatchLowercase,Numbers=OldStyle}
% \setmainfont[Mapping=tex-text,Ligatures={Common,Rare,TeX},Scale=MatchLowercase,Numbers=OldStyle]{Alegreya}
% \setsansfont[Mapping=tex-text,Ligatures={Common,Rare,TeX},Scale=MatchLowercase,Numbers=OldStyle]{Alegreya Sans}

% % \setmainfont[Ligatures = TeX, Scale = MatchLowercase, Numbers = OldStyle]{Alegreya}
% % \setsansfont[Numbers={OldStyle,Lowercase,Proportional},Ligatures={Common,Rare,TeX},Style=Historic]{Alegreya Sans}
% \setmonofont{DejaVuSansMono}
% % % \setmathfont{TeXGyreDejaVuMath}
% % \setmathfont{TeXGyreDejaVuMath-Regular}

% \usepackage{xunicode,xltxtra,url,parskip}
% \usepackage[usenames,dvipsnames]{xcolor}






% \documentclass[10pt,twocolumn]{revtex4}
% \usepackage[a4paper,margin=0.2cm]{geometry}

% %\usepackage{fontspec} % optional
% \usepackage{newtxtext,newtxmath}


% \usepackage{hyperref} % Required for adding links   and customizing them
% \definecolor{linkcolour}{RGB}{229,57,53} % Link color
% \hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Mohamed Bana's Curriculum Vitae},
  pdfauthor={Software Engineer},
  colorlinks=true,
  linkcolor={red},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Mohamed Bana's Curriculum Vitae}
\author{Software Engineer}
\date{}

\begin{document}
\maketitle

% \usepackage{hyperref} % Required for adding links and customizing theme

\hypersetup{
  pdftitle={Mohamed Bana's Curriculum Vitae},
  pdfauthor={Mohamed Bana},
  pdfcreator={Mohamed Bana},
  pdfproducer={Mohamed Bana},
}

% \usepackage[pdftex,
%             pdfauthor={Your Name},
%             pdftitle={The Title},
%             pdfsubject={The Subject},
%             pdfkeywords={Some Keywords},
%             pdfproducer={Latex with hyperref, or other system},
%             pdfcreator={pdflatex, or other tool}]{hyperref}
\definecolor{linkcolour}{RGB}{229,57,53} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\urlstyle{same}

% \renewcommand\UrlFont{\bfseries\itshape}
\renewcommand\UrlFont{\bfseries}

\setstretch{0.1}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.6343}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.3657}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Contact}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
\textbf{Web}
\end{minipage} \\
\midrule()
\endhead
\href{tel:+44-07960-045-281}{+44-07960-045-281} &
\url{https://github.com/mbana} \\
\href{mailto:jobs@bana.io}{\nolinkurl{jobs@bana.io}} &
\url{https://linkedin.com/in/mbana} \\
\url{https://stackoverflow.com/users/241993/mohamed-bana} &
\url{https://bana.io/blog} \\
\bottomrule()
\end{longtable}

I am a highly skilled Software Engineer with over a decades worth of job
experience and a proven record. I love to build and maintain
high-availability rock-solid systems that support successful businesses.
I am looking for an interesting \textbf{remote-only} job, solo or in a
small team of professionals to share my knowledge and to learn from.
Part-time occupation is negotiable. Please read my cover letter at
\url{https://bana.io/resume/cover-letter}.

\hypertarget{work-experience}{%
\subsection{Work Experience}\label{work-experience}}

\hypertarget{software-engineer-and-director-banaio-ltd.-london-united-kingdom---032017present}{%
\subsubsection{\texorpdfstring{Software Engineer and Director,
\href{https://bana.io}{BanaIO Ltd.}, London, United Kingdom -
03/2017--Present}{Software Engineer and Director, BanaIO Ltd., London, United Kingdom - 03/2017--Present}}\label{software-engineer-and-director-banaio-ltd.-london-united-kingdom---032017present}}

Software Engineer and Director at BanaIO Ltd.~Worked at several
companies and projects:

\begin{itemize}
\tightlist
\item
  Cynergy Bank
\item
  Vitrifi
\item
  IBM
\item
  Open Banking
\item
  Ninety Percent of Everything
\item
  Root Capital LLP
\item
  Lloyds Banking Group
\end{itemize}

Tech: Golang, Kubernetes, Docker, Docker Compose, Linux, Shell
scripting/Bash, Google Cloud Platform (GCP) and Google Kubernetes Engine
(GKE).

\hypertarget{senior-software-engineer-kubeshop-greenwich-united-states---052022012023}{%
\subsubsection{\texorpdfstring{Senior Software Engineer,
\href{https://kubeshop.io/}{Kubeshop}, Greenwich, United States -
05/2022--01/2023}{Senior Software Engineer, Kubeshop, Greenwich, United States - 05/2022--01/2023}}\label{senior-software-engineer-kubeshop-greenwich-united-states---052022012023}}

Worked on \href{https://docs.kusk.io/}{\texttt{kusk-gateway}}, a
OpenAPI-driven API Gateway for Kubernetes. Links:

\begin{itemize}
\tightlist
\item
  \url{https://kusk.kubeshop.io/} or \url{https://kusk.io}
\item
  \url{https://github.com/kubeshop/kusk-gateway}
\end{itemize}

Kusk is a Kubernetes API gateway powered by Envoy. The main difference
with other API Gateways is that Kusk has native support for OpenAPI.

Modern REST APIs are developed using OpenAPI specification that is then
used to generate API documentation, tests, server stubs and clients all
from the OpenAPI definition. Kusk enables the use of OpenAPI definitions
to configure the Ingress Controller of your Kubernetes clusters.

The commits I made against the repository is available to view at:
\url{https://github.com/kubeshop/kusk-gateway/commits?author=mbana}.

Tech: Golang, Kubernetes, Kubernetes Control Plane,
\href{https://github.com/envoyproxy/go-control-plane}{\texttt{go-control-plane}},
\href{https://www.envoyproxy.io/}{Envoy Proxy}, Docker, Docker Compose,
Minikube, Shell scripting/Bash, gRPC, Protocol Buffers, GitHub
Workflows, Linux.

\hypertarget{software-engineer-paymentsense-limited-london-uk---072021102021}{%
\subsubsection{\texorpdfstring{Software Engineer,
\href{https://www.paymentsense.com}{Paymentsense Limited}, London, UK -
07/2021--10/2021}{Software Engineer, Paymentsense Limited, London, UK - 07/2021--10/2021}}\label{software-engineer-paymentsense-limited-london-uk---072021102021}}

I worked with Golang on \texttt{Connect-E}
(\url{https://docs.connect.paymentsense.cloud/ConnectE/GettingStarted}).

Tech: Golang with modules, Docker, Docker Compose, TypeScript, GCP,
Google Cloud Datastore, Google Cloud Big Query, Google Cloud Pub / Sub.

\hypertarget{senior-front-end-software-engineer-synthace-ltd.-london-uk---042016112016}{%
\subsubsection{\texorpdfstring{Senior Front-End Software Engineer,
\href{https://synthace.com}{Synthace Ltd.}, London, UK -
04/2016--11/2016}{Senior Front-End Software Engineer, Synthace Ltd., London, UK - 04/2016--11/2016}}\label{senior-front-end-software-engineer-synthace-ltd.-london-uk---042016112016}}

Did a fair amount of architectural UI work:

\begin{itemize}
\tightlist
\item
  JWT-based authentication: Implemented most, if not all, of the
  authentication related UI features. Polymer didn't have an
  authentication module as it's fairly new requiring me to re-implement
  this feature.
\item
  API interactions: I introduced Swagger JS and did the conversion from
  plain XHR to Promises, and ensured API was in-sync with the state of
  the authentication.
\item
  Updates via the Web Socket for notifications and async task updates:
  STOMP Over WebSocket.
\item
  Bootstrapped the testing using Web Component Tester.
\item
  Deciding on the build, test and hosting strategy, e.g., hosting our
  own CDN using Azure.
\item
  Performance: 1) pushed to have HTTP/2 enabled, and prototyped, on our
  custom server written in Go, 2) implemented lazy-loading of our Web
  Components which are included using HTML Imports, 3) Significantly
  improved UI build scripts; went from a somewhat un-deterministic build
  to one that almost always runs.
\item
  Introduced ES6 to the code-base, and moving to defining Polymer
  elements using ES6 classes.
\item
  Misc: libraries/utils to ease UI development.
\end{itemize}

We deploy Docker images to our Kubernetes cluster running in Azure
using:

\begin{itemize}
\tightlist
\item
  Docker: Fairly comfortable using this.
\item
  Kubernetes: I've done deployments of dev branches, so I understand the
  deployment model, navigating the Kubernetes dashboard and crude
  command line interactions, e.g., port-forwarding of the service the
  pod is running from the cluster to the local machine.
\end{itemize}

Added support our language called Antha to Monaco Editor, the editor
that powers Visual Studio Code.

Since this is a startup I have done a fair amount of work and I have
been given a fair share of responsibility, more so than any of my prior
roles.

Tech: JavaScript, ES6, \href{https://www.polymer-project.org}{Polymer
Project}, \href{https://www.webcomponents.org}{Web Components},
TypeScript, VSCode, Azure, Docker, Kubernetes, Go,
\href{https://github.com/Polymer/web-component-tester}{Polymer Web
Component Tester}, Git, Swagger.

\hypertarget{software-engineer-ig-index-ltd.-london-uk---09-2014022016}{%
\subsubsection{\texorpdfstring{Software Engineer,
\href{https://www.ig.com/uk}{IG Index Ltd.} London, UK -
09-2014--02/2016}{Software Engineer, IG Index Ltd. London, UK - 09-2014--02/2016}}\label{software-engineer-ig-index-ltd.-london-uk---09-2014022016}}

\hypertarget{price-indicator-alerts}{%
\paragraph{Price \& Indicator Alerts}\label{price-indicator-alerts}}

My main responsibility was handling the UI aspect---setting,
configuring, triggering---of the various Alerts we support, from the
basic Price Alert to Technical Indicators such as RSI and Moving
Average. \textbf{Tech New:} Modern UI powered by ES2015 (Babel),
Ember.js, Handlebars and Less. The UI was then composed of isolated and
reusable Ember components. Runs on a NodeJS server, managed with npm and
bower, and version controlled using Git. Integration and unit tests
written in Mocha then run using Karma. \textbf{Tech Old:} Vanilla
JavaScript using an in-house framework when changing the previous UI.

\hypertarget{charts}{%
\paragraph{Charts}\label{charts}}

Assisted in the conversion of the Adobe Flex Real Time Charts to an
SVG-based version. Tech: d3 and tested like above.

\hypertarget{deeplinking}{%
\paragraph{Deeplinking}\label{deeplinking}}

A hashed action link, like typical deeplinks, that we send to our
Clients which then launches the mobile IG app, or directs them to the
app store for the device with the IG app pre-selected. Upon login the
action is carried out automatically. I did the bulk of the work with the
team lead overseeing it. Tech: Java 8, Spring and acceptance tested
using Cucumber. Redirecting and launching of the IG app was done using
vanilla JavaScript.

\hypertarget{software-engineer-itrs-international-trading-room-software-group-ltd.-london-uk---02-201009-2014}{%
\subsubsection{\texorpdfstring{Software Engineer,
\href{https://www.itrsgroup.com}{ITRS (International Trading Room
Software) Group Ltd.} London, UK -
02-2010--09-2014}{Software Engineer, ITRS (International Trading Room Software) Group Ltd. London, UK - 02-2010--09-2014}}\label{software-engineer-itrs-international-trading-room-software-group-ltd.-london-uk---02-201009-2014}}

\hypertarget{javascript-ui-software-engineer---012014092014}{%
\paragraph{JavaScript (UI) Software Engineer -
01/2014--09/2014}\label{javascript-ui-software-engineer---012014092014}}

UI for the next generation of the product which is built around, loosely
speaking, a real-time distributed analytics store. The aim is for the
old system to stream data to the new system so we can provide all the
great visualizations available in the HTML ecosystem, which was not
achievable in a reasonable amount of time in Swing.

The code is entirely modularized using RequireJS so we can test each
viewmodel without creating a view, we then test the entire UI
(end-to-end tests) using WebDriverJS.

Some Java/C coding required to write NodeJS bindings to interact with
the store. We evaluated several frameworks, Angular, Batman and
KnockoutJS, by writing prototype applications that connected to our
backend for a period of roughly 4-6 months before we chose to settle on
Knockout.js.

Tech: JavaScript, NodeJS, Node-WebKit, Durandal, KnockoutJS, RequireJS,
Git, Jasmine, Protractor (WebDriverJS), Jenkins, Bower, HTML5, CSS,
LoopBack.io.

\hypertarget{java-ui-software-engineer---072012122013}{%
\paragraph{Java (UI) Software Engineer -
07/2012--12/2013}\label{java-ui-software-engineer---072012122013}}

Worked with two software engineers and one QA member on a new Swing UI,
ACLite, that uses our new streaming-based API to access Geneos data, for
more info. see \url{https://resources.itrsgroup.com/OpenAccess}. We
access data from a fault-tolerant Cluster that is built on a set of
distributed nodes. The system we coded against is somewhat similar to
the Amazon distributed key/value store, DynamoDB, except with support
for streaming, so I am familiar with dealing with distributed systems.

Tech: Java, Maven, Swing, Eclipse, Jenkins, Git, Vagrant.

\hypertarget{c-software-engineer---022010062012}{%
\paragraph{C++ Software Engineer -
02/2010--06/2012}\label{c-software-engineer---022010062012}}

Spent one year with Run The Business (RTB) team, a team set-up to fix
critical bugs that Customers encounter. A very challenging role which
requires all-around product knowledge, good debugging skills and being
able to liaise with our Support staff in dealing with the Customers.
Prior to this I was one of three software engineers working in the
Transactions and Latency Monitoring team (part of the backend team)
doing core C++. We wrote and maintained the following plug-ins that are
part of the Geneos suite:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://docs.itrsgroup.com/docs/geneos/5.1.0/Netprobe/trading_fix/fix.html}{Geneos
  FIX plug-in}: Monitors FIX (protocol) messages.
\item
  \href{https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/feedadapter_ug.html}{Feed
  Latency Monitoring Plug-In}: Monitors feeds and calculates latency of
  instruments and fields across the monitored feeds.
\item
  \href{https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/latency_monitoring/message_tracker/fix_adapter.html}{Latency
  Monitoring - Message Tracker FIX adapter}: Tracks, generally, FIX
  messages across several checkpoints.
\item
  \href{https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/mdm_ug.html}{Market
  Data Monitor}: See below. And bespoke plug-ins written for specific
  firms.
\end{enumerate}

We also maintained several non-finance specific plug-ins. I ported
another bespoke plug-in called Price Latency Monitor (provides latency
figures for bonds) to MS VC++ when I worked on this team. Projects:

\begin{itemize}
\tightlist
\item
  I converted the Windows version of the entire product suite from
  Visual Studio 2005 to 2010.
\item
  I wrote the Market Data Reliability plug-in. This plug-in connects to
  the Patsystem's Trading API to monitor commodity prices, using their C
  API, to determine if prices are `stale'.
\item
  I ported a significant part of our product to Solaris x86-64 (64-bit
  non-sparc architecture).
\end{itemize}

Tech: C++, STL, Boost, Visual Studio, Linux/Unix, GDB, DBX, Make,
Configure, XML, XPath, CPPUnit,
\href{https://en.wikipedia.org/wiki/Financial_Information_eXchange}{Financial
Information eXchange (FIX) protocol},
\href{https://docs.itrsgroup.com/docs/geneos/5.1.0/Netprobe/trading_fix/fix.html}{Geneos
FIX plug-in},
\href{https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/feedadapter_ug.html}{Feed
Latency Monitoring Plug-In},
\href{https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/latency_monitoring/message_tracker/fix_adapter.html}{Latency
Monitoring - Message Tracker FIX adapter},
\href{https://docs.itrsgroup.com/docs/geneos/5.2.0/Netprobe/market_data_monitoring/mdm_ug.html}{Market
Data Monitor},
\href{https://docs.itrsgroup.com/docs/geneos/5.1.0/Netprobe/trading_pats/pats-status.html}{Geneos
PATS-STATUS Plug-In}, \href{www.patsystems.com}{Patsystem's Trading
API}.

\hypertarget{software-engineer-internship-then-tester-thomson-reuters.-london-uk---05-200911-2009}{%
\subsubsection{Software Engineer Internship, then Tester, Thomson
Reuters. London, UK -
05-2009--11-2009}\label{software-engineer-internship-then-tester-thomson-reuters.-london-uk---05-200911-2009}}

\hypertarget{c-software-engineer}{%
\paragraph{C\# Software Engineer}\label{c-software-engineer}}

One of four software engineers working on a search and navigation
interface to Global Product Search. Full life-cycle of development;
requirements engineering, analysis and design to implementation, testing
and deployment.

Tech: C\#, Silverlight 3.0, MS SQL Server 2005, LINQ, Web Services
(WCF), XML and Visual Studio 2008. I handled deployment using
CruiseControl.NET.

\hypertarget{tester}{%
\paragraph{Tester}\label{tester}}

User Acceptance Testing of the latest release of Thomson Reuter's 3000
Extra, then called UTAH, now called Eikon. UTAH combines the data from
Thomson and Reuters. My primary responsibilities were to validate the
end product against pre-defined requirements/workflows. 1. Worked on
Thomson Reuters project UTAH as part of a large team. 2. Tasks included
testing, observing, documenting software bugs, issues and errors before
final release of Utah. 3. Testing was done over multiple iterations.

\hypertarget{education}{%
\subsection{Education}\label{education}}

\begin{itemize}
\tightlist
\item
  \textbf{2005-2008:} BSc Computer Science, City, University of London.
\item
  \textbf{2008-2009:} MSc Software Systems Engineering, University
  College London, and Trading \& Financial Market Structure module,
  London Business School.
\end{itemize}

\hypertarget{additional-information}{%
\subsection{Additional Information}\label{additional-information}}

\hypertarget{misc}{%
\subsubsection{Misc}\label{misc}}

\begin{itemize}
\tightlist
\item
  \textbf{Passport/Nationality:} I am a British citizen with a British
  passport.
\item
  \textbf{Drivers Licence:} Full UK Driving Licence.
\end{itemize}

\hypertarget{languages}{%
\subsubsection{Languages}\label{languages}}

\begin{itemize}
\tightlist
\item
  \textbf{English and Swahili:} Native.
\item
  \textbf{Arabic:} Intermediate. I have lived in Marrakech, Morocco for
  almost two years. I have also lived in Cairo, Egypt and have travelled
  several times to the UAE.
\end{itemize}

\end{document}
