% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Mohamed Bana's Cover Letter},
  pdfauthor={I am only looking for a fully remote Golang - Senior Software Engineer - role.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Mohamed Bana's Cover Letter}
\author{I am \textbf{\emph{only}} looking for a fully remote Golang -
Senior Software Engineer - role.}
\date{}

\begin{document}
\maketitle

\setstretch{0.1}
\hypertarget{introduction-and-background}{%
\subsubsection{Introduction and
background}\label{introduction-and-background}}

I am a well-rounded Software Engineer, and I understand what it takes to
release a product having worked on the back-end, front-end, testing and
finally the deployment aspect of several products.

A role involving web technologies hosted on a cloud-based backend. I've
worked on all the tiers of a software product, so I can appreciate the
different concerns expressed at each level. What interests me: Go/Golang
backends, building frontends in JavaScript, complete end-to-end testing
of the final project, CI builds on the cloud, deployment on the cloud
using Google Cloud Platform (GCP), containerising software using Docker,
and orchestrating the built containers using Kubernetes.

\hypertarget{key-skills-and-preferred-job-role}{%
\subsubsection{Key skills and preferred job
role}\label{key-skills-and-preferred-job-role}}

I'm flexible in terms of the choice of framework used, however, my ideal
role will involve the following:

\begin{itemize}
\tightlist
\item
  Go/Golang as I have good experience with this. I have been using
  Golang since 2017.
\item
  A role where Linux, Google Cloud Platform/AWS/Azure, Docker/Podman and
  Kubernetes are being used. Open Banking would be a plus.
\end{itemize}

I'm up for learning more of Rust but it's just a hobby at the moment.

\textbf{Summary:} Senior Software Engineer: Golang, Linux, Docker,
Docker-Compose, Kubernetes, Cloud Computing, Google Cloud Computing
(GCP), Fedora Linux.

\hypertarget{salary-and-notice-period}{%
\subsubsection{Salary and notice
period}\label{salary-and-notice-period}}

I'm available to start immediately. I'm willing to negotiate on this as
it depends on a few things, that said:

\begin{itemize}
\tightlist
\item
  If it's a contracting role, minimum of £500 per day outside of IR35
  and £600 per day inside of IR35.
\item
  If it's a permanent position, minimum of £90,000 per year.
\end{itemize}

The figures I mentioned above are not set in stone and I am willing to
listen to counter offers.

\hypertarget{work-locations-considered}{%
\subsubsection{Work locations
considered}\label{work-locations-considered}}

A fully remote role with a UK or US company.

\hypertarget{any-visa-restrictions-if-applicable-ilr-tier-2-dependant-visa-etc}{%
\subsubsection{Any visa restrictions -- if applicable (ILR, Tier 2,
Dependant visa
etc)}\label{any-visa-restrictions-if-applicable-ilr-tier-2-dependant-visa-etc}}

\begin{itemize}
\tightlist
\item
  \textbf{Passport/Nationality:} I am a British citizen with a British
  passport, National Insurance number etc.
\item
  \textbf{Drivers Licence:} Full UK Driving Licence.
\end{itemize}

\end{document}
