% Enable hyperlinks
\setupinteraction
  [state=start,
  title={Mohamed Bana --- Full Stack Senior Software Engineer --- Cover Letter},
  style=,
  color=,
  contrastcolor=]

% make chapter, section bookmarks visible when opening document
\placebookmarks[chapter, section, subsection, subsubsection, subsubsubsection, subsubsubsubsection][chapter, section]
\setupinteractionscreen[option=bookmark]
\setuptagging[state=start]


% use microtypography
\definefontfeature[default][default][script=latn, protrusion=quality, expansion=quality, itlc=yes, textitalics=yes, onum=yes, pnum=yes]
\definefontfeature[smallcaps][script=latn, protrusion=quality, expansion=quality, smcp=yes, onum=yes, pnum=yes]
\setupalign[hz,hanging]
\setupitaliccorrection[global, always]

\setupbodyfontenvironment[default][em=italic] % use italic as em, not slanted

\definefallbackfamily[mainface][rm][CMU Serif][preset=range:greek, force=yes]
\definefontfamily[mainface][rm][Alegreya]
\definefontfamily[mainface][mm][TeXGyreDejaVuMath-Regular]
\definefontfamily[mainface][ss][Alegreya Sans]
\definefontfamily[mainface][tt][DejaVuSansMono][features=none]
\setupbodyfont[mainface]

\setupwhitespace[medium]

\setuphead[chapter]            [style=\tfd,header=empty]
\setuphead[section]            [style=\tfc]
\setuphead[subsection]         [style=\tfb]
\setuphead[subsubsection]      [style=\bf]
\setuphead[subsubsubsection]   [style=\sc]
\setuphead[subsubsubsubsection][style=\it]

\setuphead[chapter, section, subsection, subsubsection, subsubsubsection, subsubsubsubsection][number=no]

\definedescription
  [description]
  [headstyle=bold, style=normal, location=hanging, width=broad, margin=1cm, alternative=hanging]

\setupitemize[autointro]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setupthinrules[width=15em] % width of horizontal rules

\setupxtable[frame=off]
\setupxtable[head][topframe=on,bottomframe=on]
\setupxtable[body][]
\setupxtable[foot][bottomframe=on]


\starttext
\startalignment[middle]
  {\tfd Mohamed Bana --- Full Stack Senior Software Engineer --- Cover Letter}
  \bigskip
\stopalignment

\subsection[title={Intro},reference={intro}]

I am a well-rounded Software Engineer, and I understand what it takes to
release a product having worked on the back-end, front-end, testing and
finally the deployment aspect of several products.

I am looking for a role involving web technologies hosted on a
cloud-based backend. I've worked on all the tiers of a software product,
so I can appreciate the different concerns expressed at each level. I
feel the latest trend in web technologies; quick prototyping, large
selection of libraries, ease of programming and its cross-platform
support is where the future is heading. This, distributed systems and
big data algorithms are where I am focusing my current efforts---all of
which are equally interesting to me.

\subsection[title={Background},reference={background}]

A role involving web technologies hosted on a cloud-based backend. I've
worked on all the tiers of a software product, so I can appreciate the
different concerns expressed at each level. I feel the latest trend in
web technologies; quick prototyping, large selection of libraries, ease
of programming and its cross-platform support is where the future is
heading. This, distributed systems and big data algorithms are where I
am focusing my current efforts---all of which are equally interesting to
me.

I'm a well-rounded engineer and I'm able to see the delivery, from
beginning to end, of a software stack. This includes the building,
testing and continuous delivery of the solution. I have examples in my
repos that demonstrate all these in a cloud environment:

\startitemize[packed]
\item
  Go/Golang backends.
\item
  Building frontends in JavaScript.
\item
  Complete end-to-end testing of the final project.
\item
  CI builds on the cloud.
\item
  Deployment on the cloud using Google Cloud Platform (GCP).
\item
  Containerising software using Docker.
\item
  Orchestrating the built containers using Kubernetes.
\stopitemize

\subsubsection[title={Technology Stack},reference={technology-stack}]

I'm flexible in terms of the choice of framework used, however, my ideal
role will involve (any of) the following:

\startitemize[packed]
\item
  Backend: Ideally Go/Golang as I have good experience with this.
\item
  Frontend: JavaScript or any language that targets JavaScript on the
  frontend side, my ideal choice would be TypeScript. I would prefer to
  use Vue.js as the underlying framework that the UI is built with.
\item
  Roles where Linux, Google Cloud Platform/Azure/AWS, Docker and
  Kubernetes are being used. Open Banking would be a plus.
\item
  I'm up for learning more of Rust. It's just a hobby at the moment.
\stopitemize

\subsubsection[title={Enumeration and Job
Preferences},reference={enumeration-and-job-preferences}]

\startitemize[packed]
\item
  {\bf Rate:} I'm seeking a daily rate of >£580 per day. I'm willing to
  negotiate on this.
\item
  {\bf Location:} I'm looking for work in the UK, ideally in London as
  that is where I mainly live.
\item
  {\bf Start Date:} I'm available to start immediately.
\item
  {\bf Job Type:} I've a limited company called BANAIO LTD which I
  started in March 2017 and I've been a contractor since then. I would
  prefer to stick to contracting but I will also consider a permanent
  position.
\stopitemize

Kind regards,

Mohamed Bana

\thinrule

\useURL[url1][https://bana.io][][\type{https://bana.io}]\from[url1] ---
\useURL[url2][mailto:m@bana.io][][m@bana.io]\from[url2] ---
+44-7960-045-281

\stoptext
